---
title: "simpleRegress"
author: "Kayleen Hernandez"
date: "11-02-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

We are comparing the variables chest and the variable Neck to see what variable is better at determining length.


## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck is a variable for determining a bears length had adjusted R- square score of 0.7476

The scatter plot shows that as neck size goes up, Length does as well, therefore neck size is a good predictor to determine length of the bear. 

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```

## Numerical Summary 

```{r}
cor(bears$LENGTH,bears$NECK)
```
the correlation coefficient


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
``` 

CHEST as a variable for determining a bears length and adjusted R- square score of 0.7869

The scatter plot shows that as CHEST size goes up, length does as well, therefore CHEST size is a good predictor to determine the length of a bear. 


## Numerical Summary 

```{r}
cor(bears$LENGTH,bears$CHEST)
```
The correlation coefficient 

## Conclusion

Chest had an adjusted r squared score of 0.7869 while NECK had an adjusted r squared score of 0.7476

Chest is a better predictor of lenght than neck is because the adjusted r squared of the fir for CHEST was larger than the adjusted R squared of the fit for NECK
