---
title: "simpleRegress"
author: "Kayleen Hernandez"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

We are comparing the variables chest and the variable Neck to see what variable is better at determining length.


## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck is a variable for determining a bears length had adjusted R- square score of 0.7476

The scatter plot shows that as neck size goes up, Length does as well, therefore neck size is a good predictor to determine length. 

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```

## Numerical Summary 

```{r}
cor(bears$LENGTH,bears$NECK)
```
the correlation coefficient


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
``` 

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
``` 

Chest is a variable for determining a bears length had adjusted R- squared of 0.7476

The scatter plot shows that as chest size goes up length does as well therefore chest size is a good predictor to determine the length of a bear. 


## Numerical summary 


```{r}
cor(bears$LENGTH,bears$CHEST)
```


the correlation coefficient

## Conclusion

chest had an adjusted r squared score of 



Chest is a better variable to use to predict for the length of bears because the adjusted r squared test shows for chest is at 0.7869. The adjusted R squared of the fit for NECK. 
